\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-27 paper.qmd
Updated true model with less sample..for better vis

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 10

@@

two_curvy_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#3182bd") +
  geom_point(
    #size = 0.2,
    alpha = 0.3,
    color = "#000000") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("a", cex = 2) +
  theme(
    legend.position = "none"
  )

@@

two_curvy_proj_tsne_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#3182bd") +
  geom_point(
    #size = 0.2,
    alpha = 0.3,
    color = "#000000") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.125, 0.075)) + 
  ylim(c(-0.125, 0.075)) +
  interior_annotation("b", c(0.08, 0.93), cex = 2) +
  theme(
    legend.position = "none"
  )
```

@@

>>>>

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 6

@@

two_curvy_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#253494") +
  geom_point(
    #size = 0.2,
    alpha = 0.3,
    color = "#969696") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("a", cex = 2) +
  theme(
    legend.position = "none"
  )

proj_plot_two_curvy_true <- model_df |>
  ggplot(
    aes(
      x = proj1_from, 
      y = proj2_from)) +
  geom_point(
    color = "#000000") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("a", cex = 2) +
  theme(
    legend.position = "none"
  )

@@

two_curvy_proj_tsne_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#253494") +
  geom_point(
    #size = 0.2,
    alpha = 0.3,
    color = "#969696") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.125, 0.075)) + 
  ylim(c(-0.125, 0.075)) +
  interior_annotation("b", c(0.08, 0.93), cex = 2) +
  theme(
    legend.position = "none"
  )
```

@@

```{r}
#| echo: false
#| label: fig-predict-two-curvy
#| fig-pos: H
#| fig-width: 9
#| fig-height: 5
#| fig-cap: "Comparison of prediction generated using the exiting `umap` prediction method and our method: (a) A view of the true model in projections from $7\\text{-}D$, (b) predicted data from the `umap` prediction method, (c) predicted data from our method, and (d) comparison of predictions from both methods. In plot (d), points representing the same data but predicted by different methods are connected by lines. Need to add concluded sentence after changing the data."

# proj_plot_two_curvy_true + plot_predict_umap_two_curvy + 
#   plot_predict_umap_two_curvy + plot_predict_umap_connect_two_curvy +
#   plot_layout(ncol = 4)
proj_plot_two_curvy_true
```

### 2024-09-27 paper.tex
Updated true model with less sample..for better vis

>>>>

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-predict-two-curvy-1.pdf}

\caption{\label{fig-predict-two-curvy}Comparison of prediction generated
using the exiting \texttt{umap} prediction method and our method: (a) A
view of the true model in projections from \(7\text{-}D\), (b) predicted
data from the \texttt{umap} prediction method, (c) predicted data from
our method, and (d) comparison of predictions from both methods. In plot
(d), points representing the same data but predicted by different
methods are connected by lines. Need to add concluded sentence after
changing the data.}
